### 2013-07-24 doc/asplos14/memory.tex
edits and todos
Rework memory section to use `asyncronous` instead of non-blocking.

\paragraph{Global memory access} 
Access to \Grappa's distributed shared memory is provided through  {\em
delegate\/} operations, which are short memory accesses performed at the memory
location's home node. When the data access pattern has
low-locality, it is more efficient to modify the data on its home core rather
than bringing a copy to the requesting core and returning it after
modification. Delegate operations~\cite{Nelson:hotpar11, delegated:oopsla11}
provide this capability. Applications can dispatch computation to be performed
on individual machine-word sized chunks of global memory to the memory system
itself. Delegates can execute arbitrary non-blocking code, so we use them to perform simple
\emph{read\/}/\emph{write\/} operations to global memory, as well as more complex \emph{read-modify-write\/} operations (e.g., \emph{fetch-and-add\/}).

@@

Delegate operations can be either {\em blocking\/} or {\em non-blocking}.
With blocking operations, the task issuing the delegate call blocks until
the delegate operation completes, which is necessary, for example, to ensure
that synchronization has finished before continuing. Synchronization in \Grappa
is implemented using blocking delegate operations. On the other hand, remote data
accesses often can overlap. In order to avoid
unnecessary waiting, we support non-blocking delegate operations. For reads,
we support a ``futures''-like mechanism. Tasks may issue delegate reads in
parallel and block on the ``promises'' returned by non-blocking delegate
invocations. Delegate write operations may also be performed as
non-blocking,
and since they do not return data, a mechanism to detect completion is needed.
\Grappa provides a \texttt{GlobalCompletionEvent} synchronization object, which non-blocking operations (including tasks) can be enrolled with and which other tasks can block on to be notified and woken when all enrolled operations in the collection are complete.
\TODO{augment this with our bulk futures ie global completions}

>>>>

\paragraph{Global memory access} 
Access to \Grappa's distributed shared memory is provided through  {\em
delegate\/} operations, which are short memory accesses performed at the memory
location's home node. When the data access pattern has
low-locality, it is more efficient to modify the data on its home core rather
than bringing a copy to the requesting core and returning it after
modification. Delegate operations~\cite{Nelson:hotpar11, delegated:oopsla11}
provide this capability. Applications can dispatch computation to be performed
on individual machine-word sized chunks of global memory to the memory system
itself.
Delegates can execute arbitrary code, provided they do not block, to ensure communicator workers make progress. Provided they touch only memory owned by a single core, we can use them to perform simple
\emph{read\/}/\emph{write\/} operations to global memory, as well as more complex \emph{read-modify-write\/} operations (e.g., \emph{fetch-and-add\/}). We use these primitive operations to implement higher-level synchronization mechanisms such as mutexes, condition variables, and full-empty bits.

@@

Delegate operations can be either {\em blocking\/} or {\em asynchronous}.
With blocking operations, the task issuing the delegate call blocks until
the delegate operation completes, which is necessary, for example, to ensure
that synchronization has finished before continuing. On the other hand, remote data
accesses often can overlap, and delegates with no return value may not need to block the caller. 
To avoid unnecessary waiting, we support asynchronous delegate operations. For reads,
we support a ``futures''-like mechanism which allows tasks to issue reads in parallel and block on the ``promises'' returned. Delegate write operations may also be performed asynchronously, but synchronization is still needed to ensure that asynchronous operations have completed.
\Grappa provides a \texttt{GlobalCompletionEvent} synchronization object, which asyncronous operations (including tasks) can be enrolled. Tasks can block on these objects to be woken when all enrolled operations are complete.
% \TODO{augment this with our bulk futures ie global completions}
